### 2023-10-08 README.Rmd
Update citation information
Update handle [no ci]

<!-- badges: start -->
[![R-CMD-check](https://github.com/chainsawriot/rang/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/rang/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

Chan CH, Schoch D (2023) rang: Reconstructing reproducible R computational environments. arXiv preprint:[2303.04758](https://doi.org/10.48550/arXiv.2303.04758)

@@

``` r
remotes::install_github("chainsawriot/rang")
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/gesistsa/rang/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/gesistsa/rang/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

Chan CH, Schoch D (2023) rang: Reconstructing reproducible R computational environments. PLOS ONE [https://doi.org/10.1371/journal.pone.0286761](https://doi.org/10.1371/journal.pone.0286761)

@@

``` r
remotes::install_github("gesistsa/rang")
```
